Viscous Transport in Eroding Porous Media

### 2019-10-03 docs/transport/erosion_transport.tex
modify figs in transport paper
small change

In Figure~\ref{fig:Eroding20vort}, we observe that erosion creates a
network of channels from the inlet to outlet where the velocity and
vorticity, and therefore erosion rate, are much larger than other
regions.  These channels can be further visualized by considering the
streamlines.  In Figure~\ref{fig:Eroding20tracer}, we freeze the
geometry at the second snapshot from Figure~\ref{fig:Eroding20vort} and plot 200 streamlines that are initialized at $x=-1$ and equally
spaced in $y \in (-1,1)$.  The streamlines are shown at five different
times, and the final plot is a zoom in of the lower right quadrant of
the fifth time step.  Since we use a high-order quadrature rule and time
stepping method, we resolve streamlines that come very close to the
eroded bodies.  There are three clear regions where the streamlines are
most concentrated, corresponding to the regions of highest velocity.
Two of these regions are located between the bodies and the solid walls
at $y=\pm 1$, and the third cuts through the porous region with the
upper part of the channel formed by bodies 1, 4, 6, and 8.
\todo[inline]{Right now, this description has the reader looking at Fig.
8, but the bodies are not numbered in that figure, so they don't know
which ones are 1, 4, 6, 8 without flipping back and forth with the
previous figures to try to match corresponding bodes.} Since the flow is
fastest in these regions, the shearing is largest, and this causes the
channels to continue to open fastest as observed in
Figure~\ref{fig:Eroding20vort}.

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}\\
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20tracer} 200 streamlines in the second
geometry from Figure~\ref{fig:Eroding20vort}. The streamlines are
initialized at $x=-1$ and are equally spaced in $y \in (-1,1)$. The
first five snapshots are evenly spaced in time.  The bottom right frame
is a zoom in of the fifth snapshot.  Since we use the Barycentric
quadrature rule and the fourth-order Runge-Kutta method, some
streamlines are very close to the grains without penetrating them.}
\end{center}
\end{figure}

>>>>

In Figure~\ref{fig:Eroding20vort}, we observe that erosion creates a
network of channels from the inlet to outlet where the velocity and
vorticity, and therefore erosion rate, are much larger than other
regions.  These channels can be further visualized by considering the
streamlines.  In Figure~\ref{fig:Eroding20tracer}, we freeze the
geometry at the second snapshot from Figure~\ref{fig:Eroding20vort} and plot 200 streamlines that are initialized at $x=-1$ and equally
spaced in $y \in (-1,1)$.  The streamlines are shown at five different
times, and the final plot is a zoom in of the lower right quadrant of
the fifth time step.  Since we use a high-order quadrature rule and time
stepping method, we resolve streamlines that come very close to the
eroded bodies.  There are three clear regions where the streamlines are
most concentrated, corresponding to the regions of highest velocity.
Two of these regions are located between the bodies and the solid walls
at $y=\pm 1$, and the third cuts through the porous region with the
upper part of the channel formed by bodies 1, 4, 6, and 8.  Since the
flow is fastest in these regions, the shearing is largest, and this
causes the channels to continue to open fastest as observed in
Figure~\ref{fig:Eroding20vort}.

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30n}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90n}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150n}\\
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210n}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270n}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270n_zoom}
\caption{\label{fig:Eroding20tracer} 200 streamlines in the second
geometry from Figure~\ref{fig:Eroding20vort}. The streamlines are
initialized at $x=-1$ and are equally spaced in $y \in (-1,1)$. The
first five snapshots are evenly spaced in time.  The bottom right frame
is a zoom in of the fifth snapshot.  Since we use the Barycentric
quadrature rule and the fourth-order Runge-Kutta method, some
streamlines are very close to the grains without penetrating them.}
\end{center}
\end{figure}
